---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "85%",
  dpi = 300,
  fig.align = "center"
)
```

# voters

<!-- badges: start -->
[![CodeFactor](https://www.codefactor.io/repository/github/jvieroe/voters/badge)](https://www.codefactor.io/repository/github/jvieroe/voters)
[![R-CMD-check](https://github.com/jvieroe/voters/workflows/R-CMD-check/badge.svg)](https://github.com/jvieroe/voters/actions)
[![License: GPL (>= 3)](https://img.shields.io/badge/license-GPL (>= 3)-blue.svg)](https://cran.r-project.org/web/licenses/GPL (>= 3))
[![](https://img.shields.io/github/last-commit/https://github.com/jvieroe/voters.svg)](https://github.com/https://github.com/jvieroe/voters/commits/main)
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

# Introduction

The purpose of `voters` is to provide easy access to data on Danish polling stations.


## Usage

Download data on Danish polling stations using the `voters::getPS()` function:

```{r warning=F, message=F}
library(voters)
```

```{r warning=F, message=F}
df <- getPS()
df
class(df)
```
As a default, data is downloaded as a spatial dataset of type `"sf", "tibble"`. To download a non-spatial version simply use the `spatial` argument:
```{r warning=F, message=F}
df <- getPS(spatial = FALSE)
class(df)
```

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
if(!require("devtools")) install.packages("devtools")
library(devtools)
devtools::install_github("jvieroe/voters")
```

# Acknowledgements

* The `R` Core Team for developing and maintaining the language
* [Danmarks Adressers Web API (DAWA)](https://dawadocs.dataforsyningen.dk/)

