---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "85%",
  dpi = 300,
  fig.align = "center"
)
```

# voters

<!-- badges: start -->
[![CodeFactor](https://www.codefactor.io/repository/github/jvieroe/voters/badge)](https://www.codefactor.io/repository/github/jvieroe/voters)
[![R-CMD-check](https://github.com/jvieroe/voters/workflows/R-CMD-check/badge.svg)](https://github.com/jvieroe/voters/actions)
[![License: GPL (>= 3)](https://img.shields.io/badge/license-GPL (>= 3)-blue.svg)](https://cran.r-project.org/web/licenses/GPL (>= 3))
[![](https://img.shields.io/github/last-commit/https://github.com/jvieroe/voters.svg)](https://github.com/https://github.com/jvieroe/voters/commits/main)
[![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

# Introduction

The purpose of `voters` is to provide easy access to data on Danish polling stations.

## Terms of use
Data is provided through [Danmarks Adressers Web API (DAWA)](https://dawadocs.dataforsyningen.dk/). DAWA is developed and run by the [Danish Agency for Data Supply and Efficiency (SDFE)](https://eng.sdfe.dk/). SDFE's [terms of use](https://download.kortforsyningen.dk/content/vilk%C3%A5r-og-betingelser) apply.


## Usage

Download data on Danish polling stations using the `voters::getPS()` function:

```{r warning=F, message=F}
library(voters)
```

```{r warning=F, message=F}
df <- getPS()
df
```

As a default, data is downloaded as a spatial dataset of type `"sf", "tibble"`:

```{r warning=F, message=F}
class(df)
```

```{r warning=F, message=F}
library(ggplot2)
library(Manu)
library(ggpubr)

df %>% 
  #filter(stkreds %in% c("København", "Københavns Omegn")) %>% 
  ggplot(data = .) +
  geom_sf(aes(fill = regi),
          color = "grey90",
          size = .0000000001) +
  scale_fill_manual(values = Manu::get_pal("Takahe"),
                      name = "") +
  theme_void() +
  ggpubr::theme_transparent()

```

To download a non-spatial version simply use the `spatial` argument:

```{r warning=F, message=F}
df_raw <- getPS(spatial = FALSE)
class(df_raw)
```

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
if(!require("devtools")) install.packages("devtools")
library(devtools)
devtools::install_github("jvieroe/voters")
```

# Acknowledgements

* [Danmarks Adressers Web API (DAWA)](https://dawadocs.dataforsyningen.dk/) for the data and the API functionality
* Frederik Hjorth ([fghjorth](http://fghjorth.github.io/)) and Bo Schwartz Madsen ([BoSchwartz](https://twitter.com/boschwartz?lang=en)) for development ideas
* The `R` Core Team for developing and maintaining the language

